---
title: "intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bvbrcGoldStd)
```

All datasets below are cleaned, reviewed metadata loaded with
`loadGoldStdData(dataset = ...)`. Source is BV-BRC by default; any other
source (e.g. NCBI) is called out explicitly in the dataset name. See each
folder's README for file-level detail:
[`cleaned_hosts/`](https://github.com/JRaviLab/bvbrcGoldStd/blob/main/inst/extdata/cleaned_hosts/README.md),
[`cleaned_isolationsource/`](https://github.com/JRaviLab/bvbrcGoldStd/blob/main/inst/extdata/cleaned_isolationsource/README.md),
[`cleaned_drugs/`](https://github.com/JRaviLab/bvbrcGoldStd/blob/main/inst/extdata/cleaned_drugs/README.md),
[`cleaned_geography/`](https://github.com/JRaviLab/bvbrcGoldStd/blob/main/inst/extdata/cleaned_geography/README.md).

Wide tables are shown with `dplyr::glimpse()`; narrow ones with a
`knitr::kable()` preview of the first few rows.

## Hosts

`host` is cross-checked against BV-BRC; `host_ncbi` is NCBI-only.

```{r}
dplyr::glimpse(loadGoldStdData("host"))
dplyr::glimpse(loadGoldStdData("host_ncbi"))
```

## Isolation source

```{r}
knitr::kable(head(loadGoldStdData("isolation_source")))
```

## Drugs

```{r}
knitr::kable(head(loadGoldStdData("drug_class")))
```

## Geography

`geography` reads the flat file; `bvbrc_countries_clean` is the same table
as a lazy-loaded package dataset (`data(bvbrc_countries_clean)`,
documented at `?bvbrc_countries_clean`).

```{r}
dplyr::glimpse(loadGoldStdData("geography"))
dplyr::glimpse(bvbrc_countries_clean)
```
